\subsection{Lifetime Expectancy Calculations}
To perform the required lifetime expectancy calculations, some
assumptions about the stochastic behaviour of the microcontrollers are
made. An assumption that was provided by the problem text, was that
the expected lifetime of a single microcontroller was six years. In
addition to this, we assumed that the lifetime of each microcontroller
followed an exponential probability distribution, and that their
individual lifetimes are independent. 

The first assumption is made because the exponential distribution is
simple to use for calculations. Even though it is not suitable for
describing the lifetime of an entire technical device, it is used
extensively in reliability theory\cite{wikipedia}. Thus, it should
providing an estimate of how the system behaves. It was also suggested
by the course staff.

The second assumption is also somewhat optimistic, since the
microcontrollers are exposed to the same environmental hazards at the
same time. For instance, a solar flare will most likely strike all the
microcontrollers simultaneously, and thus microcontroller lifetimes
are likely to have a non-zero covariance. The assumption is still made
to make the calculations easier. If a more accurate model is
desirable, dependence should be taken into account.

With these assumptions, $f(t) = \frac{1}{6}e^{-\frac{1}{6}t}$ is the
probability density function of a failure event for an individual
microcontroller, and $F(t) = 1 - e^{-\frac{1}{6}t}$ is the
corresponding cumulative distribution giving the probability that the
microcontroller has failed within time $t$. Consequently, we can
define $P(t) := 1 - F(t) = e^{-\frac{1}{6}t}$ to be the probability
that the microcontroller has not failed within time $t$. Assuming as
we have that each microcontroller is independent, we can view the
potential of failure within a given time as a Bernoulli trial for each
of the microcontrollers. Consequently, the probability that exactly
$r$ microcontrollers have not failed within time $t$, as a function of
$t$, is given by $Q(r) = \binom{4}{r}P(t)^4(1 - P(t))^{4 - r})$. With
this framework, we can begin answering the questions stated in
\autoref{sec:problem}.

\subsubsection{Calculation of Probability of Error in Maximum One Controller}
\label{sec:errorinmaxone}
The probability that at most one controller has failed is the
probability that either four or three controllers are still
working. Since these two events are independent---there cannot be both
exactly four and exactly three microcontrollers that are still working
at a point in time---the total probability is the sum of the
probability of each event. Hence, the probability of an error in at
most one controller within a given time $t$ is given by

\begin{align*}
    Q(4) + Q(3) &= \binom{4}{4}P(t)^4 + \binom{4}{3}P(t)^3(1 - P(t)) \\
                &= (e^{-\frac{t}{6}})^4  + 4 (e^{-\frac{t}{6}})^3(1 - e^{-\frac{t}{6}}) \\
                &= e^{-\frac{4}{6}t} + 4e^{-\frac{t}{2}}(1-e^{-\frac{2}{3}t}) \\
                &= e^{-\frac{2}{3}t} + 4e^{-\frac{1}{2}t} - 4e^{-\frac{2}{3}t} \\
                &=
    \tikzmarkin[black]{a}
         4e^{-\frac{1}{2}t} - 3e^{-\frac{2}{3}t}
  \tikzmarkend{a}\\
\end{align*}

\subsubsection{Calculation of Probability of Error in Maximum Two Controllers}
\label{sec:errorinmaxtwo}
This probability is the same as the probability that either exactly
four, exactly three or exactly two microcontrollers are still working
by time $t$. By the same logic as given in
\autoref{sec:errorinmaxone}, this is the same as
\begin{align*}
  &Q(4) + Q(3) + Q(2) \\
  &=\binom{4}{4}P(t)^4 + \binom{4}{3}P(t)^3(1 - P(t)) + \binom{4}{2}P(t)^2(1 - P(t))^2 \\
  &= 4e^{-\frac{1}{2}t} - 3e^{-\frac{2}{3}t} + 6e^{-\frac{1}{3}t}(1-e^{-\frac{t}{6}})^2\\
  &= 4e^{-\frac{1}{2}t} - 3e^{-\frac{2}{3}t} + 6e^{-\frac{1}{3}t}(1-2e^{-\frac{t}{6}} + e^{-\frac{t}{3}})\\
  &= 4e^{-\frac{t}{2}} - 3e^{-\frac{2}{3}t} + 6e^{-\frac{1}{3}t} - 12e^{-\frac{t}{2}} + 6e^{-\frac{2}{3}t}\\
  &=
  \tikzmarkin[black]{b}
        6e^{-\frac{t}{3}} + 3e^{-\frac{2}{3}t} - 8e^{-\frac{1}{2}t}
  \tikzmarkend{b}\\
\end{align*}

This function describes the probability that the system is still alive
within time $t$. For future reference, we shall denote it as $R(t)$.

\subsubsection{Calculation of Probability in At Least Three Controllers}
\label{sec:errorinatleastthree}
At least three controllers being broken within time $t$ is the
complement of the event that at most two controllers have failed
within time $t$. Thus, this probability is simply the negation of the
result derived in \autoref{sec:errorinmaxtwo}, which is
\begin{align*}
  1 - R(t) &= 1 - (Q(4) + Q(3) + Q(2)) \\
           &= 1 - (6e^{-\frac{t}{3}} + 3e^{-\frac{2}{3}t} - 8e^{-\frac{1}{2}t}) \\
           &=
  \tikzmarkin[black]{c}
           8e^{-\frac{1}{2}t} - 6e^{-\frac{t}{3}} - 3e^{-\frac{2}{3}t} + 1
  \tikzmarkend{c}\\
\end{align*}

\subsubsection{Mean Time to Failure}
The mean time to system failure is the expected value of a stochastic
variable $X$ denoting time until at least three microcontrollers have
failed. Now, $Prob\{X \le t\} = Prob\{\text{System has failed within
  time } t\}$, so the cumulative distribution function of $X$,
$F_X(t)$, is given by the result in
\autoref{sec:errorinatleastthree}. If we denote the probability
density function of $X$ by $f_X(t) = \frac{\partial}{\partial
  t}F_x(t)$, we get that

\begin{align*}
  E[X] &= \int_0^{\infty}tf_X(t)dt = \int_0^{\infty}t\frac{\partial}{\partial t} F_X(t)dt \\
       &= \lim_{b \to \infty}[tF_X(t)]_{0}^b - \int_0^{\infty}F_X(t)dt \\
       &= \lim_{b \to \infty}[tF_X(t)]_0^b - \int_0^{\infty}1 - R(t)dt \\
       &= \lim_{b \to \infty}[tF_X(t)]_0^b - \int_0^\infty1dt + \int_0^{\infty}R(t)dt \\
       &= \lim_{b \to \infty}[tF_X(t)]_0^b - \lim_{b \to \infty}[t]_0^b + \int_0^{\infty}R(t)dt \\
       &= \lim_{b \to \infty}(bF_X(b) - 0F_X(0)) - \lim_{b \to \infty}(b - 0) + \int_0^{\infty}R(t)dt \\
       &= \lim_{b \to \infty}bF_X(b) - \lim_{b \to \infty}b + \int_0^{\infty}R(t)dt \\
       &= \lim_{b \to \infty}b\lim_{b \to \infty}F_X(b) - \lim_{b \to \infty}b + \int_0^{\infty}R(t)dt \\
       &= \lim_{b \to \infty}(b - b) + \int_0^{\infty}R(t)dt \\
       &= \int_0^{\infty}R(t)dt \\
       &= \int_0^{\infty}6e^{-\frac{t}{3}} + 3e^{-\frac{2}{3}t} - 8e^{-\frac{1}{2}t}dt \\
       &= [-18e^{-\frac{t}{3}} - \frac{9}{2}e^{-\frac{2}{3}t} + 16e^{-\frac{1}{2}t}]_0^{\infty} \\
       &= 0 - (-18 - \frac{9}{2} + 16) = 18 + \frac{9}{2} - 16 \\
       &=
  \tikzmarkin[black]{d}
       6.5\text{ years}
  \tikzmarkend{d}\\
\end{align*}

Thus, the expected life time of the entire system is 6.5 years. This
is an increase of only $8.33 \%$ from the expected life time of a
system with a single microcontroller. However, as space launches are
expensive, it might be worth the extra cost of redundancy and liaison
development to increase the life time of the system as much as
possible. It is also an added benefit that the microcontroller
failures are reported together with the data, so that it is possible
to know the status of the system.

%\begin{align*}
%x = 3
%Q(4) + Q(3) &= P(t)^4 + \binom{4}{3}P(t)^3(1 - P(t)) 
%             &= (e^{\frac{t}{6}})^4  + 4 (e^{\frac{t}{6}})^3(1 - e^{\frac{t}{6}})

%%%%%\end{align*}

\subsection{Alternative Voting Algorithms}
One of the major goal on this task was to optimize for area useage. In
order to achieve the most efficient solution regarding LUT useage, we
came up with three fundamentally different solutions for the voting
process. Except for the solution described in \autoref{sec:design},
the two other designs were as follow:

\subsubsection{Bit Counter}
One of the alternate designs were based on a counter. For each
microcontroller, if a controller was not tagged, and its data value
was high, the counter was incremented. Otherwise, if the
microcontroller had low output (and still not tagged), the counter was
decremented. The output of
the voting module was\\\hspace*{.3in}{\ttfamily if cnt > 0 then 1 else 0}\\
This assures that the majority vote of the working microcontrollers
are output, and 0 if the vote is a tie.

This algorithm was easy to understand, it was flexible regarding
number of microcontrollers, and it was easy to be convinced that the
design worked properly. A major disadvantage was that the counter used
a lot of LUTs, required for the integer addition and comparison. In
addition, to count just the values from the active microcontrollers
two auxilliary four bit vectors were created. To calculate each bit a
LUT was required, so this used eight LUTs. In total the system used 19
LUTs without output selection and ECC, while the current solution uses
13 without these modules enabled. The estimated clock frequency was
280 MHz, while the current system has an estimate of 306 MHz. It was
therefore also slower, and although this metric could not have tipped
the scales as the most important design goal was area it made it clear
that the current solution was the best alternative. The code for the
bit counter implementation can be found in \autoref{apx:bitcnt}

\subsubsection{Lookup Table}
In the search for another method to do the voting, we decided to build
a lookup table using a simple VHDL switch statement in which the
expression for the majority vote was looked up for each possible
configuration of error tags. This code can be seen in
\autoref{apx:table}. The idea was to give the synthesis tool as much
freedom as possible in doing the mapping of the expression onto the
4-input LUTs on the Xilinx FPGA. Using this solution, we got got 17
LUTs for the system without output selection and ECC, with an
estimated clock frequency of 271.3 MHz. The synthesis tool was
therefore either not clever enough in its processing of the VHDL code,
or we had been unable to write an expression that was sufficiently
easy to interpret or nonstrict in the case of don't care
conditions. An advantage of this solution was that it was very easy to
read, so it might be worth spending more time on tweaking the
expressions to fit the synthesiser. This might, however, reduce the
clarity of the expression. A disadvantage of this solution compared to
the bit counter, is that it is not as flexible since adding a
microcontroller would require doubling the number of cases and
creating more complex subexpressions within the blocks.

\subsection{Alternative Overall Design Strategies}
The way our Liaison System was implemented used a strictly serial
datapath through the system. This was done due to the thought that a
serial design was faster and simpler than an equal but parallel
design. However, it would have been possible to use a serial to
parallel converter and stack up the voted results simultaneously as
they were outputed. This would give us an easier-to-understand ECC
calculation, since we could have described the parity bits directly as
equations of the data bits they cover. This would, however, most
likely not have reduced the area usage or given us a faster
design. Instead of complexity in combining the parity bit enable
signals, complexity would have arisen in the combinatoin of the data
bits. Since the same number of LUTs are required for combining the
seven data bits covered by each parity bit as the 

In the current design, the voting and the error tagging of the
microcontrollers are done separatly. It would have been possible to
calculate error tags simultainiously with voting the data, but we did
not get enought time to test the impact of this approach.

\subsection{Possible Simplifications of Current Implementation}

\paragraph{SECDED-bit Simplification} \hfill \\
As explained in \autoref{sec:implementation}, the computation of the
SECDED bit is split into counting the parity for all the data bits
while they are being sent, and performing and XOR of all the ECC
flip-flops when sending it. Instead of performing this XOR operation
with the parity bits themselves, one can exploit the fact that the
parity bits are simply an XOR of data bits to express the overall
parity bit just in terms of data bits. To see this, let $d(i)$ denote
data bit $i$ and $p(j)$ denote parity bit $j$.  Then, by substituting
the equation for calculating $p(0)$ into the equation for $p(4)$, we
get
\begin{align*}
  p(4) &= d(0) \otimes d(1) \otimes \ldots \otimes d(10) \otimes p(0) \otimes p(1) \otimes p(2) \otimes p(3) \\
  &= d(0) \otimes d(1) \otimes \ldots \otimes d(10) \otimes \\
  & \qquad (d(0) \otimes d(1) \otimes d(3) \otimes d(4) \otimes d(6)
  \otimes d(8) \otimes d(10)) \otimes p(1) \otimes p(2) \otimes p(3) \\
  &= d(2) \otimes d(5) \otimes d(7) \otimes d(9) \otimes p(1) \otimes p(2) \otimes p(3)
\end{align*}

This substitution and simplification could be done with any desirable
combination of parity bits to shift the work between performing XOR
operations with parity bits during the output stage or calculating
state-enable signals during the data parity count accumulation
stage. By experimenting with different combinations, it might be
possible to find a configuration which yields a better
result than the current solution with no simplification does. 

\paragraph{Weaker Assumptions of Microcontroller Data Lines Validity} \hfill \\
In our design, we made the assumption that we should not use the input
data from the microcontrollers to update the error tags outside of
periods in which they were actually sending a word to the Liaison. If
this restriction was relaxed, we would be able to remove a few
flip-flops. The flip-flop containing the enable signal, for instance,
would be of no use. It would also be able to shift the responsibility
of making the circuit sequential from the input stage to the output
stage --- instead of using flip-flops for storing the input data from
the microcontrollers, we could use a flip-flop for maintaining the
value of the output signals. Since there would no longer be a need to
avoid updating error tags during a clock period, the prohibiting issue
of enabling the voter for the first data bit would no longer be
present. Since there are only two output signals and four input
signals, this would require two flip-flops less.

\todo[inline]{Is this correct? Could we not have flip flops on output now as well? We would just have to update the enable register in a different way.. but wait, it would have to be set when di\_ready is high!}

